%% MAIN DOCUMENT FOR MASTER THESIS
\documentclass[twoside,english, a4paper, 12pt]{shared/uiofysmaster}
\usepackage[top=1.5in, bottom=1.5in, left=1in, right=1in]{geometry}


% le righe importanti
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
\addbibresource{bibliography/bibthesis.bib} % qui metti il path del file .bib 

%% TITLE
\author{Lorenzo Speri}
\title{\bf{Analyzing Gravitational Waves through Numerical Simulations of Compact Binaries}}
\date{Supervisor:
Bruno Giacomazzo\\
July 2018}

%% LOAD PACKAGES
\input{shared/preamble}






%% MAIN DOCUMENT BEGINNING
\begin{document}

% LOAD COMMANDS
\input{shared/custom_commands}
\maketitle
\clearpage
\thispagestyle{empty}
\tableofcontents
\pagebreak

\afterpage{
\pagestyle{empty}
\newpage~\newpage~
%\setcounter{page}{2}
}

%% ABSTRACT AND ACKNOWLEDGMENTS
\begin{abstract1}
The observation of gravitational waves marks the beginning of a new era for studying the Universe.
The gravitational radiation plays a crucial role in the theoretical predictions of General Relativity and in the study of violent astrophysical processes, such as compact binary mergers. 
Therefore, we derive the gravitational wave solutions from the Einstein's field equation and we elucidate the implications of the theoretical predictions using different approaches.
Solving the linearized Einstein's field equation, we show that the gravitational radiation produced by a source scales as $1/r$. \\
We present simulations of equal-mass compact binaries with quasi-equilibrium initial conditions.
The gravitational waves produced by black hole binaries with six different quasi-equilibrium initial configurations are studied analyzing the differences between the evolution of the systems.
We investigate the evolution of a binary neutron star system, and we relate the rest mass density evolution to the gravitational wave signal.
We explain the communual characteristics of the gravitational waves of black hole and neutron star binaries, and we briefly explain the differences between the nature of such astronomical objects.
The theoretical prediction, that the angular frequency of the gravitational wave is twice the orbital angular frequency of the rotating binary, is confirmed by the simulations through a Fourier analysis of the gravitational signal.\\
The source code and parameters used for the simulations are publicly available, and they are all based on the open-source Einstein Toolkit code.  
This not only makes it possible to re-run and re-analyze our data, but also enables others to start future researches from this work.
\end{abstract1}
\setcounter{page}{1}


\clearpage
\section{Introduction}
\input{introduction/intro.tex}


\clearpage
\section{From the Einstein's Field Equation\\ to Gravitational Wave solutions}
\label{from_equation_to_solution}
\input{einstein_eq/einstein_eq_gw.tex}

\clearpage
\section{Effects of Gravitational Waves}
\label{effects_gw}
\input{effects_gw/ef_gw.tex}

\clearpage
\section{Production of Gravitational Waves}
\label{production_gw}
\input{production_gw/prod_gw.tex}

\clearpage
\section{Numerical Evolution of Compact Binaries}
\label{numerical_evolution}
\input{numerical_evolution/num_ev.tex}

\clearpage
\section{Conclusions}
\input{conclusion/conclusion.tex}


%% APPENDICES
\clearpage
\section*{Acknowledgements}
\input{appendix/ack.tex}

%% MAKE BIBLIOGRAPHY
%\bibliographystyle{unsrt}
\clearpage
\printbibliography


%% AND SO WE END
\end{document}

